COG-ED Manuscript

### 2021-11-16 06_Paper/COG-ED/Manuscript.Rmd
tried computing the pipeline loop but weird NAs come up

  for (i in 1:length(pipeline_data)) {

@@

          # the second decision is the type of transformation

@@

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemean + 3 * pipesd)
                                                               & pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))), ]

          } else if (pipeline_name[[1]][4] == "T") {

            pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]
          }

@@

@@

@@

@@

  #------old version below---

  # one data frame without transformations is a simple copy of the original data frame
  # put that data frame in a list in which all data frames will be and replace the RTs of incorrect trials with NA

  pipelines_data <- list("RNN" = data_nback)
  pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 0] <- NA

  # add raw version without post-error trials

  pipelines_data[["RNE"]] <- pipelines_data[["RNN"]][-c(which(pipelines_data[["RNN"]]$correct == 0) + 1), ]

  # add raw versions with 0-200ms exclusion

  pipelines_data[["RTN"]] <- pipelines_data[["RNN"]][-c(which(pipelines_data[["RNN"]]$rt < 0.2)), ]
  pipelines_data[["RTE"]] <- pipelines_data[["RTN"]][-c(which(pipelines_data[["RTN"]]$correct == 0) + 1), ]

  # group 1: across subjects, across conditions

    # raw versions

    tempmean <- mean(pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 1])
    tempsd <- sd(pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 1])

    pipelines_data[["AAR2N"]] <- pipelines_data[["RNN"]][c(which(pipelines_data[["RNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["RNN"]]$rt > (tempmean-2*tempsd))), ]
    pipelines_data[["AAR2E"]] <- pipelines_data[["AAR2N"]][-c(which(pipelines_data[["AAR2N"]]$correct == 0) + 1), ]
    pipelines_data[["AAR3N"]] <- pipelines_data[["RNN"]][c(which(pipelines_data[["RNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["RNN"]]$rt > (tempmean-3*tempsd))), ]
    pipelines_data[["AAR3E"]] <- pipelines_data[["AAR3N"]][-c(which(pipelines_data[["AAR3N"]]$correct == 0) + 1), ]

    # log transformed versions

    pipelines_data[["AALNN"]] <- pipelines_data[["RNN"]]
    pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1] <- log10(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])

    tempmean <- mean(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])
    tempsd <- sd(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])

    pipelines_data[["AALNE"]] <- pipelines_data[["AALNN"]][-c(which(pipelines_data[["AALNN"]]$correct == 0) + 1), ]
    pipelines_data[["AAL2N"]] <- pipelines_data[["AALNN"]][c(which(pipelines_data[["AALNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AALNN"]]$rt > (tempmean-2*tempsd))), ]
    pipelines_data[["AAL2E"]] <- pipelines_data[["AAL2N"]][-c(which(pipelines_data[["AAL2N"]]$correct == 0) + 1), ]
    pipelines_data[["AAL3N"]] <- pipelines_data[["AALNN"]][c(which(pipelines_data[["AALNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AALNN"]]$rt > (tempmean-3*tempsd))), ]
    pipelines_data[["AAL3E"]] <- pipelines_data[["AAL3N"]][-c(which(pipelines_data[["AAL3N"]]$correct == 0) + 1), ]

    # inverse transformed versions

    pipelines_data[["AAINN"]] <- pipelines_data[["RNN"]]
    pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1] <- 1/(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])

    tempmean <- mean(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])
    tempsd <- sd(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])

    pipelines_data[["AAINE"]] <- pipelines_data[["AAINN"]][-c(which(pipelines_data[["AAINN"]]$correct == 0) + 1), ]
    pipelines_data[["AAI2N"]] <- pipelines_data[["AAINN"]][c(which(pipelines_data[["AAINN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AAINN"]]$rt > (tempmean-2*tempsd))), ]
    pipelines_data[["AAI2E"]] <- pipelines_data[["AAI2N"]][-c(which(pipelines_data[["AAI2N"]]$correct == 0) + 1), ]
    pipelines_data[["AAI3N"]] <- pipelines_data[["AAINN"]][c(which(pipelines_data[["AAINN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AAINN"]]$rt > (tempmean-3*tempsd))), ]
    pipelines_data[["AAI3E"]] <- pipelines_data[["AAI3N"]][-c(which(pipelines_data[["AAI3N"]]$correct == 0) + 1), ]

    # square root transformed versions

    pipelines_data[["AASNN"]] <- pipelines_data[["RNN"]]
    pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1] <- sqrt(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])

    tempmean <- mean(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])
    tempsd <- sd(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])

    pipelines_data[["AASNE"]] <- pipelines_data[["AASNN"]][-c(which(pipelines_data[["AASNN"]]$correct == 0) + 1), ]
    pipelines_data[["AAS2N"]] <- pipelines_data[["AASNN"]][c(which(pipelines_data[["AASNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AASNN"]]$rt > (tempmean-2*tempsd))), ]
    pipelines_data[["AAS2E"]] <- pipelines_data[["AAS2N"]][-c(which(pipelines_data[["AAS2N"]]$correct == 0) + 1), ]
    pipelines_data[["AAS3N"]] <- pipelines_data[["AASNN"]][c(which(pipelines_data[["AASNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AASNN"]]$rt > (tempmean-3*tempsd))), ]
    pipelines_data[["AAS3E"]] <- pipelines_data[["AAS3N"]][-c(which(pipelines_data[["AAS3N"]]$correct == 0) + 1), ]

  # group 2: across subjects, within conditions

  # group 3: within subjects, within conditions

  # group 4: within subjects, across conditions

      # create index of rows in which the level changes
      #levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))

      #for (i in 1:(length(levelindex)-1)) {

        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- log10(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- 1/(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- sqrt(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
      #}

>>>>

  for (i in 1:length(pipelines_data)) {

@@

          # the second decision is the type of transformation, depending on the third letter in the data frame name

@@

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemean + 3 * pipesd)
                                                               & pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))), ]
          }

@@

        # apply the transformations and exclusions across subjects but within levels

        for (x in 1:4) {

            # the second decision is the type of transformation, depending on the third letter in the data frame name

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])

            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
                                           & (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))) | (pipelines_data[[i]]$level != x), ]

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
                                           & (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))) | (pipelines_data[[i]]$level != x), ]
            }
        }

@@

        # apply the transformations and exclusions within subjects and within levels

        for (x in 1:4) {

          for (y in 1:length(table(pipelines_data[[i]]$subject))) {

            # save the name of the subject as a temporary variable

            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]

            # the second decision is the type of transformation, depending on the third letter in the data frame name

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                     & pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                                                                   & pipelines_data[[i]]$subject == pipesubject])

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                     & pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                                                                & pipelines_data[[i]]$subject == pipesubject])

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                     & pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                                                                  & pipelines_data[[i]]$subject == pipesubject])

            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)

              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]

              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
            }
          }
        }

@@

      # apply the transformations and exclusions within subjects but across levels

        for (y in 1:length(table(pipelines_data[[i]]$subject))) {

            # save the name of the subject as a temporary variable

            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]

            # the second decision is the type of transformation, depending on the third letter in the data frame name

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])

            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)

              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]    
            } else if (pipeline_name[[1]][4] == "3") {

              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
            }
        }

    # the 200-ms-exclusion and the post-error-exclusion are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:

    # exclude RTs fast than 200 ms after stimulus onset if the fourth letter in the data frame name is a "T"

    if (pipeline_name[[1]][4] == "T") {

      pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]

    # exclude post-error trials if the fifth letter in the data frame name is an "E"
    # also making sure that there are even any error-/post-error-rows left to perform the exclusion, otherwise you get an error message

    if (pipeline_name[[1]][5] == "E") {

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ],
             pipelines_data[[i]] <- pipelines_data[[i]])

@@
